On the solution of katabatic flows with spatially varying eddy viscosity and diffusivity

### 2016-06-23 paper_BLM.tex
last review version

% ABSTRACT
\begin{abstract}
The Nieuwstadt closed form solution for the stationary Ekman layer is generalized for katabatic flows within the conceptual framework of the Prandtl model. 
The solution is valid for spatially-varying eddy viscosity and diffusivity (O'Brien type) and constant Prandtl number $(Pr)$. 
Momentum and buoyancy transfer coefficients are specified in accordance with Monin-Obukhov similarity.
The characteristics of the solution are discussed as a function of the dimensionless model parameters $Pr$ and $\hat{z}_0 \hat{N}^2 \hat{b}_s^{-1}$, where $\hat{z}_0$ is the hydrodynamic roughness length, $\hat{b}_s$ is the imposed surface buoyancy and $\hat{N}$ is the Brunt-V\"ais\"al\"a frequency.
For the considered range of such parameters, velocity and buoyancy profiles show significant variations in both phase and amplitude of extrema with respect to the classic constant-$K$ model and a more recent approximate solution based on the Wentzel-Kramers-Brillouin (WKB) theory.
Near-wall regions are characterized by relatively stronger surface momentum and buoyancy gradients, whose magnitude is inversely proportional to $Pr$. In addition, slope-parallel momentum and buoyancy fluxes are reduced, the low-level jet (LLJ) is further displaced toward the wall, and its peak velocity strongly depends on $\hat{z}_0 \hat{N}^2 \hat{b}_s^{-1}$.

@@

Here, a closed-form solution to the Prandtl-model equations is derived on a finite domain ($\hat{z} \in [\hat{z}_0,\hat{H}]$), valid for eddy viscosity and diffusivity coefficients that are modeled as a limited range of cubic polynomials, similar to what was proposed in \citet{O'Brien1970} for the planetary boundary layer. 
The derivation is a generalization of the solution proposed in \citet{Nieuwstadt1983a}, where the Ekman-layer equations were solved for the same form of momentum transfer coefficient.
Recall that the Ekman-layer equations can be reduced to the Prandtl equations after simple changes of variables \citep{Veronis1970}. 
The solution, expressed as a combination of Gaussian hypergeometric functions, represents an exact alternative to the WKB formulation for the chosen form of the eddy diffusivities. 
Its sensitivity to variations in the parameter space are investigated here within the Monin-Obukhov framework, to provide insight on the coupling between the velocity and buoyancy fields.

>>>>

% ABSTRACT
\begin{abstract}
The Nieuwstadt closed form solution for the stationary Ekman layer is generalized for katabatic flows within the conceptual framework of the Prandtl model. 
The solution is valid for spatially-varying eddy viscosity and diffusivity (O'Brien type) and constant Prandtl number $(Pr)$. 
Momentum and buoyancy transfer coefficients are specified in accordance with Monin-Obukhov similarity.
The characteristics of the solution are discussed as a function of the dimensionless model parameters $Pr$ and $\hat{z}_0 \hat{N}^2 \hat{b}_s^{-1}$, where $\hat{z}_0$ is the hydrodynamic roughness length, $\hat{b}_s$ is the imposed surface buoyancy and $\hat{N}$ is the Brunt-V\"ais\"al\"a frequency.
For the considered range of such parameters, velocity and buoyancy profiles show significant variations in both phase and amplitude of extrema with respect to the classic constant $K$ model and a more recent approximate solution based on the Wentzel-Kramers-Brillouin theory.
Near-wall regions are characterized by relatively stronger surface momentum and buoyancy gradients, whose magnitude is inversely proportional to $Pr$. In addition, slope-parallel momentum and buoyancy fluxes are reduced, the low-level jet is further displaced toward the wall, and its peak velocity strongly depends on $\hat{z}_0 \hat{N}^2 \hat{b}_s^{-1}$.

@@

Here, a closed-form solution to the Prandtl-model equations is derived on a finite domain ($\hat{z} \in [\hat{z}_0,\hat{H}]$), valid for eddy viscosity and diffusivity coefficients that are modeled as a limited range of cubic polynomials, similar to what was proposed in \citet{O'Brien1970} for the planetary boundary layer. 
The derivation is a generalization of the solution proposed in \citet{Nieuwstadt1983a}, where the Ekman-layer equations were solved for the same form of the eddy viscosity / diffusivity parameters, and $Pr=1$.
Recall that the Ekman-layer equations can be reduced to the Prandtl equations after simple changes of variables \citep{Veronis1970}. 
The solution, expressed as a combination of Gaussian hypergeometric functions, represents an exact alternative to the WKB formulation for the chosen form of the eddy diffusivities. 
Its sensitivity to variations in the parameter space are investigated here within the Monin-Obukhov framework, to provide insight on the coupling between the velocity and buoyancy fields.
